Visual proteomics using whole-lamella 2D template matching

### 2022-04-07 figures/approach.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20cm} 
    \newcommand{\figheight}{15cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,14.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
\draw [densely dotted, red,thick] (3,14.5) -- (3,10);
\draw [densely dotted, red,thick] (3,9.2) -- (3,6.4);

@@

\draw (3.55,10.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
\draw (4.15,10.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
\draw [dimen] (D1) -- (D2) node {$D_{Beam}$};

\draw [->, very thick] (3,10) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$IS_X$} ;
\draw [->, very thick] (S1) -- (3.85,10.4) node[midway,below right] {$IS_Y$};

\node (anchor) at (6.0,14.35) {}; 
\node[labelNode] {B};

% Place nodes
\node [block] (init) at (8.0,13.35) {\textbf{START} \\ Collect overview image};
\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};

@@

\node (anchor) at (11.5,14.35) {}; 
\node[labelNode] {C};
\node[graphicNode] {\includegraphics[width=8cm]{content/images/ac_strategy.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (0.5,4.5) {}; 
\node[labelNode] {C};
\node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
\node[above = 0cm and 0cm of euc.north] {Eucentric Focus};

@@

\node (anchor) at (5.5,4.5) {}; 
\node[labelNode] {D};
\node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
\node[above = 0cm and 0cm of fff.north] {Fringe-free Focus};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (10.5,4.5) {}; 
\node[labelNode] {E};
\node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20cm} 
    \newcommand{\figheight}{20cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,19.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
\draw [densely dotted, red,thick] (3,19.5) -- (3,15.0);
\draw [densely dotted, red,thick] (3,14.2) -- (3,11.4);

@@

\draw (3.55,15.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
\draw (4.15,15.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
\draw [dimen] (D1) -- (D2) node {$D_{Beam}$};

\draw [->, very thick] (3,15) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$IS_X$} ;
\draw [->, very thick] (S1) -- (3.85,15.4) node[midway,below right] {$IS_Y$};

\node (anchor) at (6.0,19.35) {}; 
\node[labelNode] {B};

% Place nodes
\node [block] (init) at (8.0,18.35) {\textbf{START} \\ Collect overview image};
\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};

@@

\node (anchor) at (11.5,19.35) {}; 
\node[labelNode] {C};
\node[graphicNode] {\includegraphics[width=8cm]{content/images/ac_strategy.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (0.5,9.5) {}; 
\node[labelNode] {D};
\node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
\node[above = 0cm and 0cm of euc.north] {Eucentric Focus};

@@

\node (anchor) at (5.5,9.5) {}; 
\node[labelNode] {E};
\node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
\node[above = 0cm and 0cm of fff.north] {Fringe-free Focus};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (10.5,9.5) {}; 
\node[labelNode] {F};
\node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (0.5,4.5) {}; 
\node[labelNode] {G};
\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/euc_lamella1_view_morph.png}};

\node (anchor) at (5,4.5) {}; 
\node[labelNode] {H};
\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/euc_lamella1_1000px.png}};

\node (anchor) at (9.5,4.5) {}; 
\node[labelNode] {I};
\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/fff_lamella4_view_morphed.png}};

\node (anchor) at (14,4.5) {}; 
\node[labelNode] {J};
\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/fff_lamella4_1000px.png}};

### 2022-04-07 figures/crop_unblur.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20cm} 
    \newcommand{\figheight}{20cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,19.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
\draw [densely dotted, red,thick] (3,19.5) -- (3,15.0);
\draw [densely dotted, red,thick] (3,14.2) -- (3,11.4);

\tikzset{dimen/.style={<->,>=latex,thin,every rectangle node/.style={above right=0.2cm and -0.3cm,fill=white,midway,font=\sffamily}}}

\draw (3.55,15.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
\draw (4.15,15.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
\draw [dimen] (D1) -- (D2) node {$D_{Beam}$};

\draw [->, very thick] (3,15) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$IS_X$} ;
\draw [->, very thick] (S1) -- (3.85,15.4) node[midway,below right] {$IS_Y$};

\node (anchor) at (6.0,19.35) {}; 
\node[labelNode] {B};

% Place nodes
\node [block] (init) at (8.0,18.35) {\textbf{START} \\ Collect overview image};
\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};

% Draw edges
\path [line] (init) -- (identify);
\path [line] (identify) -- (mutate);
\path [line] (mutate) -- (transfer);
\path [line] (transfer) -- (evaluate);
\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);

\node (anchor) at (11.5,19.35) {}; 
\node[labelNode] {C};
\node[graphicNode] {\includegraphics[width=8cm]{content/images/ac_strategy.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (0.5,9.5) {}; 
\node[labelNode] {D};
\node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
\node[above = 0cm and 0cm of euc.north] {Eucentric Focus};

\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (5.5,9.5) {}; 
\node[labelNode] {E};
\node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
\node[above = 0cm and 0cm of fff.north] {Fringe-free Focus};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (10.5,9.5) {}; 
\node[labelNode] {F};
\node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (0.5,4.5) {}; 
\node[labelNode] {G};
\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/euc_lamella1_view_morph.png}};

\node (anchor) at (5,4.5) {}; 
\node[labelNode] {H};
\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/euc_lamella1_1000px.png}};

\node (anchor) at (9.5,4.5) {}; 
\node[labelNode] {I};
\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/fff_lamella4_view_morphed.png}};

\node (anchor) at (14,4.5) {}; 
\node[labelNode] {J};
\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/fff_lamella4_1000px.png}};

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20.0cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \def\panelheight{4.6cm}

\node (anchor) at (0.5,9.5) {}; 
\node[labelNode] {A};
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
\node (box1) [box=red, fit=(panel), dashed] {};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_initial.png}};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_initial_alignment.png}};

\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
\node[labelNode] {B};
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_cropped.png}};
\node (box2) [box=red, fit=(panel), dashed] {};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_cropped.png}};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_cropped_alignment.png}};

\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
\node[labelNode] {C};
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
\draw[red, dashed, line width=0.8mm] ([shift={(-0.7,-1.2cm)}]panel.north east) -- 
                                     ([shift={(0.7,-1.2cm)}]panel.north west) --
                                     ([shift={(0.7,1.2cm)}]panel.south west) --
                                     ([shift={(-0.7,1.2cm)}]panel.south east) --
                                     ([shift={(-0.7,-1.2cm)}]panel.north east);

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_final.png}};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_final_alignment.png}};

### 2022-04-07 figures/lamella_images.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20.0cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

\node (anchor) at (0.5,9.5) {}; 
\node[labelNode] {A};
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
\node (box1) [box=red, fit=(panel), dashed] {};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_initial.png}};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_initial_alignment.png}};

\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
\node[labelNode] {B};
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_cropped.png}};
\node (box2) [box=red, fit=(panel), dashed] {};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_cropped.png}};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_cropped_alignment.png}};

\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
\node[labelNode] {C};
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
\draw[red, dashed, line width=0.8mm] ([shift={(-0.7,-1.2cm)}]panel.north east) -- 
                                     ([shift={(0.7,-1.2cm)}]panel.north west) --
                                     ([shift={(0.7,1.2cm)}]panel.south west) --
                                     ([shift={(-0.7,1.2cm)}]panel.south east) --
                                     ([shift={(-0.7,-1.2cm)}]panel.north east);

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_final.png}};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_final_alignment.png}};

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20.0cm} 
    \newcommand{\figheight}{5cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

\node (anchor) at (0.5,4.5) {}; 
\node[labelNode] {A};
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer000.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer001.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer002.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer003.png}};

\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer005.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer006.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer007.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer008.png}};

### 2022-04-07 figures/lamella_motion_thickness.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

\node (anchor) at (0.5,9.5) {}; 
\node[labelNode] {A};
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
\node (box1) [box=red, fit=(panel), dashed] {};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_initial.png}};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_initial_alignment.png}};

\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
\node[labelNode] {B};
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_cropped.png}};
\node (box2) [box=red, fit=(panel), dashed] {};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_cropped.png}};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_cropped_alignment.png}};

\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
\node[labelNode] {C};
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
\draw[red, dashed, line width=0.8mm] ([shift={(-0.7,-1.2cm)}]panel.north east) -- 
                                     ([shift={(0.7,-1.2cm)}]panel.north west) --
                                     ([shift={(0.7,1.2cm)}]panel.south west) --
                                     ([shift={(-0.7,1.2cm)}]panel.south east) --
                                     ([shift={(-0.7,-1.2cm)}]panel.north east);

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_final.png}};

\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_final_alignment.png}};

>>>>

\node (anchor) at (0.5,9.5) {}; 
\node[labelNode] {A};
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_euc_lamella1.png}};
\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_euc_lamella2.png}};
\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_euc_lamella3.png}};
\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_euc_lamella4.png}};

\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_fff_lamella1.png}};
\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_fff_lamella2.png}};
\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {};
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_fff_lamella3.png}};
\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_fff_lamella4.png}};
\node (anchor) at ([shift={(-1.0cm,4.0cm)}]panel.north east) {}; 
\node[graphicNode] (key) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_colorbar.png}};

\node (anchor) at ([shift={(0.0cm,-1.0cm)}]0.5,0 |- panel.south) {}; 
\node[labelNode] {B};
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella1.png}};
\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella2.png}};
\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella3.png}};
\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella4.png}};

\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella1.png}};
\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella2.png}};
\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella3.png}};
\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella4.png}};
\node (anchor) at ([shift={(-1.0cm,4.0cm)}]panel.north east) {}; 
\node[graphicNode] (key) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_colorbar.png}};
